Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-14 main.tex
additional theorem

\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T$. Recursive application of the volume formula shows 
    \begin{align*}
        \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
    \end{align*}
    where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T)$. Now, 
    \begin{align*}
        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
    \end{align*}
    The first estimate follows. 
    On the other hand, 
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
        .
    \end{align*}
    The second estimate follows. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, Lemma~\eqref{lemma:affinetransform} and the first estimate imply 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \diam(T_1)
        \diam(T_2)^{-1}
        \\&
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \kappa(T_1) 
        \diam(F)
        \diam(T_2)^{-1}
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \kappa(T_1) 
        .
    \end{align*}
    All the desired results thus follow.
\end{proof}

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
    Let $T_0, T_1, \dots, T_m$ be a shelling.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
    and such that for each $T_{m} \in \calT$ in the shelling
    we have the following recursive estimate: 
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
%         &
%         \leq  
%         C_{{\rm PF},\Gamma,k,p}(\calT) 
%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
%         \Cfive{n}{k}(\calT)^{k+1} 
%         \diam(T)^{k} 
%         \| \cartan u \|_{L^{p}(U_{m-1})}
%         \\&\qquad
%         + 
%         C_{{\rm PF},\Gamma,k,p}(\calT) 
%         \diam(T)^{k} 
%         \| \cartan u      \|_{L^{p}(T_{m})} 
%         \\&\qquad
%         + 
%         \Cdetsechs{n}{k}(\calT)^{-\frac 1 p} 
%         \Cfive{n}{k}(\calT)^{k} 
%         \| w \|_{L^{p}(U_{m-1})}
%         \\
        &
        \leq  
        C_{{\rm PF},\Gamma,k,p}(\calT) 
        \diam(T)^{k} 
        \left( 
            \| \cartan u      \|_{L^{p}(T_{m})} 
            +
            \Cfive{n}{k}(\calT)^{k+1} 
            \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
            \| \cartan u \|_{L^{p}(U_{m-1})}
        \right)
        \\&\qquad
        + 
        \Cfive{n}{k}(\calT)^{k} 
        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(U_{m-1})}
        .
    \end{align*}
\end{theorem}

\begin{proof}
    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
    By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
    We write $\Omega_m := \cup_{j=0}^{m} T_m$, which is a triangulated $n$-dimensional submanifold with boundary.

@@

>>>>

\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T$. Recursive application of the volume formula shows 
    \begin{align*}
        \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
    \end{align*}
    where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T)$. Now, 
    \begin{align*}
        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
    \end{align*}
    The first estimate follows. 
    On the other hand, 
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
        .
    \end{align*}
    The second estimate follows. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, Lemma~\ref{lemma:affinetransform} and the first estimate imply 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \diam(T_1)
        \diam(T_2)^{-1}
        \\&
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \kappa(T_1) 
        \diam(F)
        \diam(T_2)^{-1}
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \kappa(T_1) 
        .
    \end{align*}
    All the desired results thus follow.

    Without loss of generality, $F$ lies in the plane of the second to last coordinates,
    so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
    After further rotation, we can assume that $z_2 = a_1 e_1 + a_2 e_2$ for some $a_1, a_2 \in \bbR$.
    If $h > 0$ is the height of $z_1$ within $T_1$, then the singular values of $\Xi$ 
    are all one with the possibe exception of the singular values of the matrix 
    \begin{align*}
        A = 
        \begin{pmatrix}
            a_1/h & 0
            \\
            a_2/h & 1
        \end{pmatrix}
    \end{align*}
    Its singular values are 
    \begin{align*}
        \sigma_{\max}
        &= 
        \frac{1}{\sqrt 2}
        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
        \\&= 
        \frac{1}{\sqrt 2}
        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
            } }
        \\&= 
        \frac{1}{\sqrt 2}
        \sqrt{ 
            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
            }
        +
        \frac{1}{\sqrt 2}
        \sqrt{ 
            \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
            }
        \\&= 
        \frac{1}{2}
        \sqrt{ 
            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
            }
        +
        \frac{1}{2}
        \sqrt{ 
            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
            }
        \\&= 
        \frac{1}{2}
        \sqrt{ 
            \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
            }
        +
        \frac{1}{2}
        \sqrt{ 
            \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
            }
        ,
        \\
        \sigma_{\min}
        &=
        \frac{1}{\sqrt 2}
        \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
        \\&= 
        \frac{1}{2}
        \sqrt{ 
            1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
            }
        -
        \frac{1}{2}
        \sqrt{ 
            1 + \frac{ a_1^2 }{h^2} - \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
            }
        .
    \end{align*}

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
    Let $T_0, T_1, \dots, T_m$ be a shelling.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
    and such that for each $T_{m} \in \calT$ in the shelling
    we have the following recursive estimate: 
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
%         &
%         \leq  
%         C_{{\rm PF},\Gamma,k,p}(\calT) 
%         \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
%         \Cfive{n}{k}(\calT)^{k+1} 
%         \diam(T)^{k} 
%         \| \cartan u \|_{L^{p}(U_{m-1})}
%         \\&\qquad
%         + 
%         C_{{\rm PF},\Gamma,k,p}(\calT) 
%         \diam(T)^{k} 
%         \| \cartan u      \|_{L^{p}(T_{m})} 
%         \\&\qquad
%         + 
%         \Cdetsechs{n}{k}(\calT)^{-\frac 1 p} 
%         \Cfive{n}{k}(\calT)^{k} 
%         \| w \|_{L^{p}(U_{m-1})}
%         \\
        &
        \leq  
        C_{{\rm PF},\Gamma,k,p}(\calT) 
        \diam(T)^{k} 
        \left( 
            \| \cartan u      \|_{L^{p}(T_{m})} 
            +
            \Cfive{n}{k}(\calT)^{k+1} 
            \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
            \| \cartan u \|_{L^{p}(U_{m-1})}
        \right)
        \\&\qquad
        + 
        \Cfive{n}{k}(\calT)^{k} 
        \Cdetsechs{n}{k}(\calT)^{\frac 1 p} 
        \| w \|_{L^{p}(U_{m-1})}
        .
    \end{align*}
    \todo{Settle the notation}
\end{theorem}

\begin{proof}
    This proof is similar to the proof of Theorem~\ref{theorem:poincarefriedrichsestimate:gradzwei}.
    By assumption, there exists a shelling $T_0, T_1, \dots, T_m$. 
    We write $\Omega_m := \cup_{j=0}^{m} T_j$, which is a triangulated $n$-dimensional submanifold with boundary.

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with a shellable triangulation $\calT$.
    Let $T_0, T_1, \dots, T_m$ be a shelling.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$ 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan u = \cartan w$ 
    such that 
    \begin{align*}
        \| w \|_{L^{p}(T_{m})}
        \leq 
        C_{\PF,T,k,p}(T_{0})
        \prod_{i=0}^{m} 
        C_{???}
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
\end{theorem}
\begin{proof}
    We prove this via induction. 
    The statement is clearly satisfied when $m=0$ because then we only consider a single simplex. 
    Let us assume that the statement is true for some integer $m-1 \geq 0$.

    We write $\Omega_{m-1} := \cup_{j=0}^{m-1} T_{j}$, 
    which is a triangulated $n$-dimensional submanifold with boundary.
    By assumption, $T_{m}$ and $\overline\Omega_{m-1}$ share the interface $\Gamma_{m} \subset \partial T_{m}$, 
    which is a collection of faces of $T_{m}$. 
    In accordance to Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ completes a star in $\calT$ around some simplex $S \subseteq T$, 
    and we let $U_{m-1} \subseteq \Omega_{m-1}$ be the complement of $T_{m}$ in that newly completed star.

    We use the bi-Lipschitz mapping $\Xi_{2} : \patch_{\calT}(S) \rightarrow U_{m-1}$ as discussed in Theorem~\ref{theorem:starreflection},
    which acts as the identity along $\partial U_{m-1} \setminus \partial T$.
    By assumption, 
    there exists $w_{m-1} \in W^{p}\Alt^{k}(\Omega_{m-1})$ 
    such that $\cartan w_{m-1} = \Xi_{2}^{-1} \cartan u$ and 
    \begin{align*}
        \| w_{m-1} \|_{L^{p}(T_{m})}
        \leq 
        C_{\PF,T,k,p}(T_{0})
        \prod_{i=0}^{m} 
        C_{???}
        \| \Xi_{2}^{-\ast} \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    Because pullback and exterior derivative commute, 
    we have $w := \Xi_{2}^{\ast} w_{m-1}$ satisfying $\cartan w = \cartan u$. 
    Moreover, the desired estimate follow from Theorem~\ref{theorem:starreflection}.
    The proof is complete. 
\end{proof}
